Planning to Save Energy: How Information Format Affects Accuracy

### 2025-04-09 poster/poster.qmd
update poster

*   **Problem:** Energy insecurity is a critical public health concern, especially among low-income households who face difficult choices and unsafe coping strategies [@bednarRecognitionResponseEnergy2020; @memmottSociodemographicDisparitiesEnergy2021]. Furthermore, residential energy use significantly contributes to climate change, necessitating sustainable solutions [@farghaliStrategiesEnergyContext2023].
*   **Gap:** While interventions exist, success hinges on communication format [@fischerFeedbackHouseholdElectricity2008]. Specifically, how do different **numerical representations (kWh, %, USD)** of energy reduction goals influence consumers' ability to create *accurate*, specific conservation plans for appliance use?
*   **Concepts & Theory:** This study draws on principles of energy literacy [@dewatersEnergyLiteracySecondary2011], reference class effects (absolute units like kWh may simplify calculations compared to relative units like % or derived units like USD) [@gigerenzerSimpleToolsUnderstanding2003; @reimerNumericCommunicationRisk2015], and the importance of procedural knowledge (knowing *how* to act on a goal) [@tonkeProvidingProceduralKnowledge2024].

@@

*   **Primary Question:** How does the format (kWh, %, USD) used to present an energy reduction goal influence the accuracy of household energy conservation planning?
*   **H1 (Reference Class):** Presenting goals in **absolute units (kWh)** will lead to higher planning accuracy compared to percentage (%) or monetary (USD) formats. 
*   **H2 (Energy Literacy):** Individuals with **higher energy literacy** will demonstrate more accurate planning, regardless of format.

@@

*   **Design:** Two online experiments (N=229 & N=190 via MTurk) using a simulated household energy planning task.
*   **Task:** Participants adjusted appliance energy use (kWh) for hypothetical families to meet a specified reduction goal.
*   **Manipulation:** Goal presentation format (Between-Subjects): **kWh** vs. **%** vs. **USD**.
*   **Exp 2 Factors:** Also varied Goal Difficulty (10/15%) & Numerical Rounding (exact/rounded).

@@

*  **Key Measures:**
    *   **Planning Accuracy:** Absolute deviation between plan reduction and the goal reduction (ordinal bins: exact, minor, large error).
    *   **Energy Literacy:** 8-item knowledge scale score [@dewatersEnergyLiteracySecondary2011].
*  **Analysis:** Bayesian mixed-effects regression (Ordinal & Linear) controlling for participant and scenario random effects: $\text{Accuracy Level} \; \text{\textasciitilde} \; \text{Reference Class} + \text{Calculator} + (1|\text{id}) + (1|\text{Family Scenario})$
* **Goal Format (H1 Supported):** Planning accuracy was significantly higher when the energy reduction goal was presented in absolute units (kWh) compared to percentages (%) or U.S. dollars (USD) across both experiments. 
    * *Exp 1:* USD (*OR* = 22.9) and % (*OR* = 4.2) formats had significantly higher odds of lower accuracy than kWh.
    * *Exp 2:* Similar significant effect for USD (*OR* = 9.68); the trend persisted for % (*OR* = 2.78), though the CI included 1.0. USD/percentage formats reduced the probability of exact matches and increased large errors compared to kWh.
* **Energy Literacy (H2 Supported):** Higher energy literacy scores were significantly associated with more accurate planning (lower error) in both experiments (Exp 1: $B$ = -2.35; Exp 2: $B$  = -3.21). (See Fig 3b).
* **Exploratory Findings (Exp 2):**
    * Using rounded numbers for prior usage slightly improved accuracy (Est. = -0.53). No effect of Goal Difficulty.

@@

![Distribution of log absolute error by goal format condition (Exp 1). Lower values indicate higher accuracy.](assets/images/fig-s1-log-dist-1.png){width="80%"}

### Figure 3

@@

\makebox[\linewidth]{%
  \begin{minipage}[t]{0.44\linewidth}
    \centering
    \subcaptionbox{Posterior predictive check for the ordinal regression model. Blue bars show the observed frequencies per accuracy level, dots represent the model predictions.\label{fig-s1-ppd}}[0.93\linewidth]{%
    \includegraphics[height=4.25in, keepaspectratio]{assets/images/fig-s1-ppd-1.png}
    }
  \end{minipage}
  \hspace{0.01em}
  \begin{minipage}[t]{0.44\linewidth}
  \centering
    \subcaptionbox{Relationship between energy literacy score and log absolute error, controlling for random effects \label{fig-s1-els}}[0.93\linewidth]{%
    \includegraphics[height=4.25in, keepaspectratio]{assets/images/fig-s1-els-1.png}
    }
  \end{minipage}
}

@@

![Distribution of log absolute error by goal format condition (Exp 2). Lower values indicate higher accuracy.](assets/images/fig-s2-log-dist-1.png){width="83%"}

<!-- ### Figure 5

@@

\makebox[\linewidth]{%
  \begin{minipage}[t]{0.44\linewidth}
    \centering
    \subcaptionbox{Posterior predictive check for the Bayesian ordinal regression model. Blue bars show the observed frequencies for each accuracy level, dots with error bars represent the model predictions.\label{fig-s2-ppd}}[0.90\linewidth]{%
    \includegraphics[height=4.25in, keepaspectratio]{assets/images/fig-s2-ppd-1.png}
    }
  \end{minipage}
  \hspace{0.01em}
  \begin{minipage}[t]{0.44\linewidth}
  \centering
    \subcaptionbox{Relationship between energy literacy score and log absolute error, controlling for random effects of participant and family scenario \label{fig-s2-els}}[0.90\linewidth]{%
    \includegraphics[height=4.25in, keepaspectratio]{assets/images/fig-s2-els-1.png}
    }
  \end{minipage}
}

\end{figure}
``` -->

@@

*   **Key Finding:** Goal format significantly impacts planning accuracy. **Presenting goals in absolute kWh is superior** to relative (%) or monetary (USD) formats, likely by simplifying calculations and reducing cognitive load [@gigerenzerSimpleToolsUnderstanding2003].
*   **Energy Literacy Matters:** Higher domain knowledge consistently predicted better planning accuracy, emphasizing the role of energy education [@canfieldPerceptionsElectricityuseCommunications2017].
*   **Limitations:** Lab simulation, short duration, self-reported calculator use.
*   **Future Directions:** Explore combining kWh format with actionable tips [@tonkeProvidingProceduralKnowledge2024]; test interactive tools/visualizations.

>>>>

*   **Problem:** Energy insecurity is a critical public health concern [@bednarRecognitionResponseEnergy2020; @memmottSociodemographicDisparitiesEnergy2021]. 
*   **Prior Work:** While interventions exist, success often hinges on communication format [@canfieldPerceptionsElectricityuseCommunications2017; @fischerFeedbackHouseholdElectricity2008], such as the use of tables vs. figures, the framing of information (e.g., savings vs. costs), and energy literacy. Many reasoning tasks involving quantities are also influenced by reference class (e.g., absolute units like kWh may simplify calculations compared to relative units like % or derived units like USD) [@gigerenzerSimpleToolsUnderstanding2003; @reimerNumericCommunicationRisk2015].

@@

*   **Primary Question:** How does the Reference class (kWh, %, USD) used to present a reduction goal influence the accuracy of energy planning?
*   **H1 (Reference Class):** Goals presented in **absolute units (kWh)** will benefit planning accuracy compared to percentage (%) or monetary (USD) formats. 
*   **H2 (Energy Literacy):** Individuals with **higher energy literacy** will demonstrate more accurate planning, regardless of format.

@@

*   **Design:** Two online experiments (N=229 & N=190 via MTurk) using a simulated household energy planning task.
*   **Planning Task:** Propose appliance energy use (kWh) for hypothetical families to meet a target reduction goal.
*   **Manipulation:** Reference Class of reduction goal (Between-Subjects): **kWh** vs. **%** vs. **USD**.
*   **Exp 2 Factors:** Goal Difficulty (10% vs. 15% reduction) and Numerical Rounding (exact vs. rounded).

@@

*  **Key Measures:**
    *   **Planning Accuracy:**  Deviation between intended reduction goal and proposed plan (ordinal bins: exact, minor, large error).
    *   **Energy Literacy:** 8-item knowledge scale score [@dewatersEnergyLiteracySecondary2011].
*  **Analysis:** Bayesian mixed-effects regression: $\text{Accuracy Level} \; \text{\textasciitilde} \; \text{Reference Class} + \text{Calculator} + (1|\text{id}) + (1|\text{Family Scenario})$
* **Effect of reference class (H1 Supported):** Smallest planning errors when reduction goal was presented in absolute units (kWh) compared to percentages (%) or dollars (USD) across both experiments. 
* **Energy Literacy (H2 Supported):** Higher energy literacy scores associated with more accurate planning (lower error) in both experiments.

@@

![Distribution of log absolute error by goal format condition (Exp 1). Lower values indicate higher accuracy.](assets/images/fig-s1-log-dist-1.png){width="85%"}

### Figure 3 - Bayesian Regression Results (Exp 1)

@@

\makebox[\linewidth]{%
  \begin{minipage}[t]{0.44\linewidth}
    \centering
    \subcaptionbox{PPC for ordinal model. Blue bars are observed frequencies per accuracy level, dots show model predictions.\label{fig-s1-ppd}}[0.93\linewidth]{%
    \includegraphics[height=4.4in, keepaspectratio]{assets/images/fig-s1-ppd-1.png}
    }
  \end{minipage}
  \hspace{0.01em}
  \begin{minipage}[t]{0.44\linewidth}
  \centering
    \subcaptionbox{Relationship between energy literacy score and log absolute error of reduction plans \label{fig-s1-els}}[0.93\linewidth]{%
    \includegraphics[height=4.4in, keepaspectratio]{assets/images/fig-s1-els-1.png}
    }
  \end{minipage}
}

@@

![Distribution of log absolute error by goal format condition (Exp 2). Lower values indicate higher accuracy.](assets/images/fig-s2-log-dist-1.png){width="85%"}

### Figure 5 - Bayesian Regression Results (Exp 2)

@@

\makebox[\linewidth]{%
  \begin{minipage}[t]{0.44\linewidth}
    \centering
    \subcaptionbox{PPC for ordinal model. Blue bars are observed frequencies per accuracy level, dots show model predictions.\label{fig-s2-ppd}}[0.90\linewidth]{%
    \includegraphics[height=4.4in, keepaspectratio]{assets/images/fig-s2-ppd-1.png}
    }
  \end{minipage}
  \hspace{0.01em}
  \begin{minipage}[t]{0.44\linewidth}
  \centering
    \subcaptionbox{Relationship between energy literacy score and log absolute error of reduction plans. \label{fig-s2-els}}[0.90\linewidth]{%
    \includegraphics[height=4.4in, keepaspectratio]{assets/images/fig-s2-els-1.png}
    }
  \end{minipage}
}

@@

*   **Key Finding:** Reference class  significantly impacts planning accuracy. **Presenting goals in absolute kWh is superior** to relative (%) or monetary (USD) formats, likely by simplifying calculations and reducing cognitive load.
*   **Energy Literacy Matters:** Higher domain knowledge consistently predicted better planning accuracy, emphasizing the role of energy education.
*   **Limitations:** Lab simulation, short duration, self-reported calculator use.

### 2025-04-09 poster/poster.tex
update poster

\usepackage[T1]{fontenc}       % Use modern font encoding
\usepackage{helvet}            % Use Helvetica clone (sans-serif)
\renewcommand\familydefault{\sfdefault} % Make sans-serif the default font family
\usepackage{graphicx}          % Required for images
\usepackage{amsmath}           % For math symbols if needed
\usepackage{amssymb}           % For math symbols if needed
\usepackage{textcomp}          % For symbols like degrees
\usepackage{xcolor}            % For color definitions
\usepackage{multicol}          % For multi-column layout
\usepackage{geometry}          % To set paper size and margins (already used by Quarto, but good practice)
\usepackage{fancyhdr}          % For headers and footers
% \usepackage{titlesec}          % For customizing section titles
\usepackage{sectsty}           % Alternative/complement to titlesec for section fonts
\usepackage{enumitem}          % For customizing lists (itemize, enumerate)
\usepackage{caption}           % For customizing figure/table captions
\usepackage{subcaption} 
\usepackage{hyperref}          % For clickable links (references, URLs)
\usepackage{tikz}              % For drawing header/footer backgrounds
\usepackage{subcaption}
\usepackage{amsfonts}
\usepackage{etoolbox}
\usepackage{titletoc}        % For table of contents customization
\usepackage[explicit]{titlesec}  % For section title customization with explicit option

@@

% --- SET BASE FONT SIZE HERE (Overrides any default/cached \normalsize) ---
\makeatletter
\renewcommand{\normalsize}{%
    \@setfontsize\normalsize{18.5pt}{22pt}% Main font size and line spacing
    \abovedisplayskip 12pt plus 3pt minus 7pt
    \abovedisplayshortskip \z@ plus 3pt
    \belowdisplayshortskip 6.5pt plus 3.5pt minus 3pt
    \belowdisplayskip \abovedisplayskip
    \let\@listi\@listI}
\makeatother

@@

\titlespacing*{\subsection}
  {0pt}               % Left margin
  {.0ex plus 0.0ex minus .0ex} % Space BEFORE title (reduced slightly)
  {0.1ex plus .1ex}   % Space AFTER title (REDUCED)

\titlespacing*{\subsubsection}
  {0pt}               % Left margin
  {0.0ex plus 0.0ex minus .2ex} % Space BEFORE title (reduced slightly)
  {0.0ex plus .02ex}   % Space AFTER title (REDUCED)

@@

\begin{itemize}
\tightlist
\item
  \textbf{Problem:} Energy insecurity is a critical public health
  concern, especially among low-income households who face difficult
  choices and unsafe coping strategies (Bednar \& Reames, 2020; Memmott
  et al., 2021). Furthermore, residential energy use significantly
  contributes to climate change, necessitating sustainable solutions
  (Farghali et al., 2023).
\item
  \textbf{Gap:} While interventions exist, success hinges on
  communication format (Fischer, 2008). Specifically, how do different
  \textbf{numerical representations (kWh, \%, USD)} of energy reduction
  goals influence consumers' ability to create \emph{accurate}, specific
  conservation plans for appliance use?
\item
  \textbf{Concepts \& Theory:} This study draws on principles of energy
  literacy (DeWaters \& Powers, 2011), reference class effects (absolute
  units like kWh may simplify calculations compared to relative units
  like \% or derived units like USD) (Gigerenzer \& Edwards, 2003;
  Reimer et al., 2015), and the importance of procedural knowledge
  (knowing \emph{how} to act on a goal) (Tonke, 2024).
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Primary Question:} How does the format (kWh, \%, USD) used to
  present an energy reduction goal influence the accuracy of household
  energy conservation planning?
\item
  \textbf{H1 (Reference Class):} Presenting goals in \textbf{absolute
  units (kWh)} will lead to higher planning accuracy compared to
  percentage (\%) or monetary (USD) formats.
\item
  \textbf{H2 (Energy Literacy):} Individuals with \textbf{higher energy
  literacy} will demonstrate more accurate planning, regardless of
  format.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Design:} Two online experiments (N=229 \& N=190 via MTurk)
  using a simulated household energy planning task.
\item
  \textbf{Task:} Participants adjusted appliance energy use (kWh) for
  hypothetical families to meet a specified reduction goal.
\item
  \textbf{Manipulation:} Goal presentation format (Between-Subjects):
  \textbf{kWh} vs.~\textbf{\%} vs.~\textbf{USD}.
\item
  \textbf{Exp 2 Factors:} Also varied Goal Difficulty (10/15\%) \&
  Numerical Rounding (exact/rounded).
\end{itemize}

@@

  \begin{itemize}
  \tightlist
  \item
    \textbf{Planning Accuracy:} Absolute deviation between plan
    reduction and the goal reduction (ordinal bins: exact, minor, large
    error).
  \item
    \textbf{Energy Literacy:} 8-item knowledge scale score (DeWaters \&
    Powers, 2011).
  \end{itemize}
\item
  \textbf{Analysis:} Bayesian mixed-effects regression (Ordinal \&
  Linear) controlling for participant and scenario random effects:
  \(\text{Accuracy Level} \; \text{\textasciitilde} \; \text{Reference Class} + \text{Calculator} + (1|\text{id}) + (1|\text{Family Scenario})\)
\item
  \textbf{Goal Format (H1 Supported):} Planning accuracy was
  significantly higher when the energy reduction goal was presented in
  absolute units (kWh) compared to percentages (\%) or U.S. dollars
  (USD) across both experiments.

  \begin{itemize}
  \tightlist
  \item
    \emph{Exp 1:} USD (\emph{OR} = 22.9) and \% (\emph{OR} = 4.2)
    formats had significantly higher odds of lower accuracy than kWh.
  \item
    \emph{Exp 2:} Similar significant effect for USD (\emph{OR} = 9.68);
    the trend persisted for \% (\emph{OR} = 2.78), though the CI
    included 1.0. USD/percentage formats reduced the probability of
    exact matches and increased large errors compared to kWh.
  \end{itemize}
\item
  \textbf{Energy Literacy (H2 Supported):} Higher energy literacy scores
  were significantly associated with more accurate planning (lower
  error) in both experiments (Exp 1: \(B\) = -2.35; Exp 2: \(B\) =
  -3.21). (See Fig 3b).
\item
  \textbf{Exploratory Findings (Exp 2):}

  \begin{itemize}
  \tightlist
  \item
    Using rounded numbers for prior usage slightly improved accuracy
    (Est. = -0.53). No effect of Goal Difficulty.
  \end{itemize}
\end{itemize}

@@

{\centering \includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{assets/images/fig-s1-log-dist-1.png}

@@

\subsubsection{Figure 3}\label{figure-3}

@@

{\centering \includegraphics[width=0.83\linewidth,height=\textheight,keepaspectratio]{assets/images/fig-s2-log-dist-1.png}

@@

@@

\begin{itemize}
\tightlist
\item
  \textbf{Key Finding:} Goal format significantly impacts planning
  accuracy. \textbf{Presenting goals in absolute kWh is superior} to
  relative (\%) or monetary (USD) formats, likely by simplifying
  calculations and reducing cognitive load (Gigerenzer \& Edwards,
  2003).
\item
  \textbf{Energy Literacy Matters:} Higher domain knowledge consistently
  predicted better planning accuracy, emphasizing the role of energy
  education (Canfield et al., 2017).
\item
  \textbf{Limitations:} Lab simulation, short duration, self-reported
  calculator use.
\item
  \textbf{Future Directions:} Explore combining kWh format with
  actionable tips (Tonke, 2024); test interactive tools/visualizations.
\end{itemize}

@@

\bibitem[\citeproctext]{ref-farghaliStrategiesEnergyContext2023}
Farghali, M., Osman, A. I., Mohamed, I. M. A., Chen, Z., Chen, L.,
Ihara, I., Yap, P.-S., \& Rooney, D. W. (2023). Strategies to save
energy in the context of the energy crisis: A review.
\emph{Environmental Chemistry Letters}, \emph{21}(4), 2003--2039.
\url{https://doi.org/10.1007/s10311-023-01591-5}

@@

\bibitem[\citeproctext]{ref-tonkeProvidingProceduralKnowledge2024}
Tonke, S. (2024). Providing procedural knowledge: {A} field experiment
to encourage resource conservation in {Namibia}. \emph{Journal of
Development Economics}, \emph{166}, 103202.
\url{https://doi.org/10.1016/j.jdeveco.2023.103202}

>>>>

\usepackage[T1]{fontenc}       % Use modern font encoding
\usepackage{helvet}            % Use Helvetica clone (sans-serif)
\renewcommand\familydefault{\sfdefault} % Make sans-serif the default font family
\usepackage{graphicx}          % Required for images
\usepackage{amsmath}           % For math symbols if needed
\usepackage{amssymb}           % For math symbols if needed
\usepackage{textcomp}          % For symbols like degrees
\usepackage{xcolor}            % For color definitions
\usepackage{multicol}          % For multi-column layout
\usepackage{geometry}          % To set paper size and margins (already used by Quarto, but good practice)
\usepackage{fancyhdr}          % For headers and footers
% \usepackage{titlesec}          % For customizing section titles
\usepackage{sectsty}           % Alternative/complement to titlesec for section fonts
\usepackage{enumitem}          % For customizing lists (itemize, enumerate)
\usepackage{caption}           % For customizing figure/table captions
\usepackage{subcaption} 
\usepackage{hyperref}          % For clickable links (references, URLs)
\usepackage{tikz}              % For drawing header/footer backgrounds
\usepackage{subcaption}
\usepackage{amsfonts}
\usepackage{etoolbox}
\usepackage{titletoc}        % For table of contents customization
\usepackage[explicit]{titlesec}  % For section title customization with explicit option
\usepackage{caption}
\captionsetup[figure]{labelformat=empty}% redefines the caption setup of the figures environment in the beamer class.

@@

% --- SET BASE FONT SIZE HERE (Overrides any default/cached \normalsize) ---
\makeatletter
\renewcommand{\normalsize}{%
    \@setfontsize\normalsize{19.5pt}{22pt}% Main font size and line spacing
    \abovedisplayskip 12pt plus 3pt minus 7pt
    \abovedisplayshortskip \z@ plus 3pt
    \belowdisplayshortskip 6.5pt plus 3.5pt minus 3pt
    \belowdisplayskip \abovedisplayskip
    \let\@listi\@listI}
\makeatother

@@

\titlespacing*{\subsection}
  {0pt}               % Left margin
  {.1ex plus 0.1ex minus .0ex} % Space BEFORE title (reduced slightly)
  {0.1ex plus .1ex}   % Space AFTER title (REDUCED)

\titlespacing*{\subsubsection}
  {0pt}               % Left margin
  {0.1ex plus 0.1ex minus .2ex} % Space BEFORE title (reduced slightly)
  {0.0ex plus .02ex}   % Space AFTER title (REDUCED)

@@

\begin{itemize}
\tightlist
\item
  \textbf{Problem:} Energy insecurity is a critical public health
  concern (Bednar \& Reames, 2020; Memmott et al., 2021).
\item
  \textbf{Prior Work:} While interventions exist, success often hinges
  on communication format (Canfield et al., 2017; Fischer, 2008), such
  as the use of tables vs.~figures, the framing of information (e.g.,
  savings vs.~costs), and energy literacy. Many reasoning tasks
  involving quantities are also influenced by reference class (e.g.,
  absolute units like kWh may simplify calculations compared to relative
  units like \% or derived units like USD) (Gigerenzer \& Edwards, 2003;
  Reimer et al., 2015).
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Primary Question:} How does the Reference class (kWh, \%, USD)
  used to present a reduction goal influence the accuracy of energy
  planning?
\item
  \textbf{H1 (Reference Class):} Goals presented in \textbf{absolute
  units (kWh)} will benefit planning accuracy compared to percentage
  (\%) or monetary (USD) formats.
\item
  \textbf{H2 (Energy Literacy):} Individuals with \textbf{higher energy
  literacy} will demonstrate more accurate planning, regardless of
  format.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Design:} Two online experiments (N=229 \& N=190 via MTurk)
  using a simulated household energy planning task.
\item
  \textbf{Planning Task:} Propose appliance energy use (kWh) for
  hypothetical families to meet a target reduction goal.
\item
  \textbf{Manipulation:} Reference Class of reduction goal
  (Between-Subjects): \textbf{kWh} vs.~\textbf{\%} vs.~\textbf{USD}.
\item
  \textbf{Exp 2 Factors:} Goal Difficulty (10\% vs.~15\% reduction) and
  Numerical Rounding (exact vs.~rounded).
\end{itemize}

@@

  \begin{itemize}
  \tightlist
  \item
    \textbf{Planning Accuracy:} Deviation between intended reduction
    goal and proposed plan (ordinal bins: exact, minor, large error).
  \item
    \textbf{Energy Literacy:} 8-item knowledge scale score (DeWaters \&
    Powers, 2011).
  \end{itemize}
\item
  \textbf{Analysis:} Bayesian mixed-effects regression:
  \(\text{Accuracy Level} \; \text{\textasciitilde} \; \text{Reference Class} + \text{Calculator} + (1|\text{id}) + (1|\text{Family Scenario})\)
\item
  \textbf{Effect of reference class (H1 Supported):} Smallest planning
  errors when reduction goal was presented in absolute units (kWh)
  compared to percentages (\%) or dollars (USD) across both experiments.
\item
  \textbf{Energy Literacy (H2 Supported):} Higher energy literacy scores
  associated with more accurate planning (lower error) in both
  experiments.
\end{itemize}

@@

{\centering \includegraphics[width=0.85\linewidth,height=\textheight,keepaspectratio]{assets/images/fig-s1-log-dist-1.png}

@@

\subsubsection{Figure 3 - Bayesian Regression Results (Exp
1)}\label{figure-3---bayesian-regression-results-exp-1}

@@

{\centering \includegraphics[width=0.85\linewidth,height=\textheight,keepaspectratio]{assets/images/fig-s2-log-dist-1.png}

@@

\subsubsection{Figure 5 - Bayesian Regression Results (Exp
2)}\label{figure-5---bayesian-regression-results-exp-2}

\makebox[\linewidth]{%
  \begin{minipage}[t]{0.44\linewidth}
    \centering
    \subcaptionbox{PPC for ordinal model. Blue bars are observed frequencies per accuracy level, dots show model predictions.\label{fig-s2-ppd}}[0.90\linewidth]{%
    \includegraphics[height=4.4in, keepaspectratio]{assets/images/fig-s2-ppd-1.png}
    }
  \end{minipage}
  \hspace{0.01em}
  \begin{minipage}[t]{0.44\linewidth}
  \centering
    \subcaptionbox{Relationship between energy literacy score and log absolute error of reduction plans. \label{fig-s2-els}}[0.90\linewidth]{%
    \includegraphics[height=4.4in, keepaspectratio]{assets/images/fig-s2-els-1.png}
    }
  \end{minipage}
}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Key Finding:} Reference class significantly impacts planning
  accuracy. \textbf{Presenting goals in absolute kWh is superior} to
  relative (\%) or monetary (USD) formats, likely by simplifying
  calculations and reducing cognitive load.
\item
  \textbf{Energy Literacy Matters:} Higher domain knowledge consistently
  predicted better planning accuracy, emphasizing the role of energy
  education.
\item
  \textbf{Limitations:} Lab simulation, short duration, self-reported
  calculator use.
\end{itemize}

@@

@@
